Tools for identifying unexpectedly low microfossil count sums

### 2020-06-16 Rmd/count_check_MS.Rmd
new pollen2

>>>>

Dataset pollen2 (Fig. \@ref(fig:multiples-plot))

```{r multiples-plot, warning = FALSE, fig.height = 100/24.5, fig.width=180/24.5, fig.cap = "A) Distribution of the percent of counts that are divisible by _k_ in each pollen assemblage with at least ten taxa. The vertical dashed line represents the 99.5% percentile. B) Percent of count in each assemblage in dataset pollen2 that are divisible by _k_ against depth. The dashed lines are the quantiles shown in part A. ", message = FALSE}
multiples_plot
```
